A partisan affair: Mapping patronage in municipal bureaucracies of Brazil

### 2021-01-12 paper/draft.tex
expand intro

In this paper, I leverage micro-level partisan information with employment data to assess the degree to which there are differential compensation structures and differences in observables among partisan and non-partisan. What I find is that the benefits of public secotr employment do not accrue to poorer voters. Rather

>>>>

In this paper, I leverage micro-level partisan information with employment data to assess the degree to which there are differential compensation structures and differences in observables among partisan and non-partisan. What I find is that the benefits of public sector employment do not accrue to poorer voters. Rather, what we see in Brazil is the accumulation of the benefits of public employment to a wealthier class of party members. Positions at higher levels of government such as executive leadership and administration are mostly allocated to party members. In contrast, less profitable offices in frontline services are less partisan.

Additionally, party members are concentrated in tenured positions. Over X\% of career bureaucrats are affiliated to a party. Party members tend to stay in the bureaucracy for longer, and receive a higher compensation than their non-partisan counterparts.
